---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# buildingpermitsurvey

<!-- badges: start -->
<!-- badges: end -->

Aims to provide uniformly formatted data from the U.S. Census Bureau's [Building
Permits Survey](https://www.census.gov/construction/bps/) for R.

Very much a work in progress. The format of the output is very likely to change!

## Installation

You can install the development version of buildingpermitsurvey like so:

``` r
devtools::install_github('kevinschaul/buildingpermitsurvey')
```

## Usage

```{r usage}
library(buildingpermitsurvey)
```

## What's implemented

### BPS by county

Years 2000-2021, annual figures

```{r county}
data("bps_annual_by_county")
dplyr::glimpse(bps_annual_by_county)
```

### BPS by metropolitan statistical area

Years 2004-2014, annual figures

```{r msa}
data("bps_annual_by_msa")
dplyr::glimpse(bps_annual_by_msa)
```
